TBD

### 2016-09-27 paper.tex
LOGCAL
LINCAL

We can easily express Eq.~\eqref{eq:logcal_amp} with the following linear system
\begin{equation}
\widetilde{\bd} = \bA\bz, 
\end{equation}
which has the following least-squares solution
\begin{equation}
\bz = (\bA^T\bA)^{-1}\bA^T\widetilde{\bd},
\end{equation}
where
\begin{equation}
\widetilde{\bd} = [\ln |d_{pq}|] \big \} ~ [pq] = 1\cdots B ~ (p<q),\nonumber\\ 
\end{equation}
and
\begin{equation}
\bA = 
\begin{bmatrix}
\coolover{{\scriptstyle j=1,\ldots,N}}{1^j_p\vee1^j_q} & \coolover{{\scriptstyle k=1,\ldots,L}\!\!\!\!}{~1_{\phi_{pq}}^k}
\end{bmatrix}
\begin{matrix}% matrix for right braces 
\coolrightbrace{1_{\phi_{pq}}^k}{[pq] = 1,\ldots,B~(p<q)}
\end{matrix}.
\end{equation}

>>>>

We can easily express Eq.~\eqref{eq:logcal_amp} with the following linear system
\begin{equation}
\widetilde{\bd} = \bA\bz, 
\end{equation}
which has the following least-squares solution
\begin{equation}
\bz = (\bA^T\bA)^{-1}\bA^T\widetilde{\bd},
\end{equation}
where
\begin{equation}
\widetilde{\bd} = [\ln |d_{pq}|] \big \} ~ [pq] = 1,\cdots,B ~ (p<q),\nonumber\\ 
\end{equation}
and
\begin{equation}
\bA = 
\begin{bmatrix}
\coolover{{\scriptstyle j=1,\ldots,N}}{\delta^j_p\vee\delta^j_q} & \coolover{{\scriptstyle k=1,\ldots,L}\!\!\!\!}{~\delta_{\phi_{pq}}^k}
\end{bmatrix}
\begin{matrix}% matrix for right braces 
\coolrightbrace{\delta_{\phi_{pq}}^k}{[pq] = 1,\ldots,B~(p<q)}
\end{matrix}.
\end{equation}

Moreover, $(*)^T$ denotes the transpose of its operand, $(*)^{-1}$ denotes matrix inversion, $\vee$ denotes the logical or operator and
\begin{equation}
\delta_y^x  = \begin{cases}
          1 & \textrm{if}~x=y\\
          0 & \textrm{otherwise}
         \end{cases}.
\end{equation}
A similar linear system can be constructed for Eq.~\eqref{eq:logcal_phase}.

\subsection{LINCAL}
\begin{equation}
c_{ij} = y_{i-j} e^{\eta_i - i \varphi_i} e^{\eta_j - i \varphi_j}
\end{equation}

\begin{eqnarray}
\frac{c_{ij}}{\partial \eta_i} &=& y_{i-j} e^{\eta_i - i \varphi_i} e^{\eta_j - i \varphi_j}\\ 
\frac{c_{ij}}{\partial \varphi_i} &=&  -i y_{i-j} e^{\eta_i - i \varphi_i} e^{\eta_j - i \varphi_j}\\
\frac{c_{ij}}{\partial \eta_j} &=& y_{i-j} e^{\eta_i - i \varphi_i} e^{\eta_j - i \varphi_j}\\ 
\frac{c_{ij}}{\partial \varphi_j} &=&  i y_{i-j} e^{\eta_i - i \varphi_i} e^{\eta_j - i \varphi_j}\\
\frac{y_{i-j}}{\partial \varphi_j} &=&  e^{\eta_i - i \varphi_i} e^{\eta_j - i \varphi_j}
\end{eqnarray}

The Wirtinger derivative is used in the last equation.

\begin{eqnarray}
c_{ij} &\approx& c_{ij}^0 + \Delta \eta_i(y_{i-j}^0 e^{\eta_i^0 - i \varphi_i^0} e^{\eta_j^0 - i \varphi_j^0}) + \Delta \eta_j(y_{i-j}^0 e^{\eta_i^0 - i \varphi_i^0} e^{\eta_j^0 - i \varphi_j^0})\\
&& -i\Delta\varphi_i (y_{i-j}^0e^{\eta_i^0 - i \varphi_i^0} e^{\eta_j^0 - i \varphi_j^0}) +i\Delta\varphi_j (y_{i-j}^0e^{\eta_i^0 - i \varphi_i^0} e^{\eta_j^0 - i \varphi_j^0})\\
&& y_{i-j}^1(y_{i-j}^0e^{\eta_i^0 - i \varphi_i^0} e^{\eta_j^0 - i \varphi_j^0})\\
&\approx&  c_{ij}^0 + e^{\eta_i^0 - i \varphi_i^0} e^{\eta_j^0 - i \varphi_j^0}(y_{i-j}^1 + y_{i-j}^0( \Delta \eta_i+ \Delta \eta_j - i\Delta\varphi_i + i\Delta\varphi_i))
\end{eqnarray}

\begin{equation}
\label{eq:residual}
r_{ij} = \delta_{ij} = c_{ij}-c_{ij}^0 = e^{\eta_i^0 - i \varphi_i^0} e^{\eta_j^0 - i \varphi_j^0}(y_{i-j}^1 + y_{i-j}^0( \Delta \eta_i+ \Delta \eta_j - i\Delta\varphi_i + i\Delta\varphi_i)) 
\end{equation}

Eq.~\ref{eq:residual} allows us to construct the following linear system:

\begin{equation}
\boldsymbol{J}[\boldsymbol{\Delta \eta},\boldsymbol{\Delta \varphi},\boldsymbol{\Delta y}]^T = \boldsymbol{r}, 
\end{equation}

where $\boldsymbol{J}$ is equal to 
\begin{equation}
\boldsymbol{J} = \bigg [\overbrace{\frac{c_{pq}}{\partial \eta_i}}^{i= 1\cdots N},~\overbrace{\frac{c_{pq}}{\partial \varphi_i}}^{i= 1\cdots N},~\overbrace{\frac{c_{pq}}{\partial y_{t}}}^{t=1\cdots r_s} \bigg ] \bigg \} [pq] = 1\cdots N_{\textrm{b}} (p<q) 
\end{equation}
or
\begin{equation}
\boldsymbol{J} = \bigg [\frac{c_{pq}}{\partial \boldsymbol{\eta}},~\frac{c_{pq}}{\partial \boldsymbol{\varphi}},~\frac{c_{pq}}{\partial \boldsymbol{y}} \bigg ] \bigg \} [pq] = 1\cdots N_{\textrm{b}} (p<q). 
\end{equation}

The last column is again a Wirtinger derivative.

Which means we can obtain the least-squares estimate as follows:

\begin{equation}
[\boldsymbol{\Delta \eta},\boldsymbol{\Delta \varphi},\boldsymbol{\Delta y}]^T = [\boldsymbol{J}^H\boldsymbol{J}]^{-1}\boldsymbol{J}^H\boldsymbol{r}.
\end{equation}
